Effect of quality-adjusted production function inputs

### 2015-04-27 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Added comments about rerunning models.

#####################################################
rerunModels=FALSE
#####################################################
@

>>>>

# Tell whether to re-run the analysis to create the models.
# This file will use previously-saved models to generate
# the paper if set to FALSE, greatly reducing time.
# If something changes in the data or in the code that
# performs the analysis, set 
# rerunModels = TRUE
# once to re-generate the information needed to 
# create the paper.
#####################################################
rerunModels=FALSE
#####################################################
@
